Learning to Dispatch: A Reinforcement Learning Framework for Train Dispatch Networks

### 2025-04-21 paper/main.tex
Fix formatting error with title

\title{Learning to Dispatch: A Reinforcement Learning Framework for Train Networks}

@@

    \end{tikzpicture}
    \caption{The reinforcement learning framework.}
    \label{fig:rl_framework}
\end{figure}

@@

    \end{tikzpicture}
    \caption{The Deep Q-Network action selection and feedback loop.}
    \label{fig:dqn_loop}
\end{figure}

>>>>

\title{Learning to Dispatch: A Reinforcement Learning Framework for Train Dispatch Networks}
\titlerunning{\textcolor{uf_blue}{Learning to Dispatch}}

@@

    \end{tikzpicture}
    \caption{The simplified markov decision process and reinforcement learning framework.}
    \label{fig:rl_framework}
\end{figure}

@@

    \end{tikzpicture}
    \caption{Simplified Deep Q-Network action selection and feedback loop.}
    \label{fig:dqn_loop}
\end{figure}
